Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-12 hotstorage13/arch.tex
w
update deletion

The representation of each snapshot in the backup storage
has a two-level index structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
A VM image is divided into a set of segments and each  segment contains hundreds of content blocks. 
These blocks are of variable-size, partitioned using
the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
The snapshot metadata  contains a list of segments and other meta data information.
Segment metadata  contains its  content block fingerprints and reference pointers. 
If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
%its content blocks are not changed as well, thus 
its segment metadata contains a reference pointer to an earlier segment.
For a dirty segment, if one of its blocks is duplicate to another block in the system,  
the block metadata contains a reference pointer to the earlier block.

@@

{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved VM snapshots and thus
expired snapshots will be deleted unless its owner explicitly asks for its retention.
We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
A block or a segment can be deleted if its reference count is zero.
%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
To delete useless  blocks or segments periodically, we read the meta data  of live 
snapshots and compute the reference count of all blocks and segments  in parallel
while following the fingerprint-based partitioning.
Similar to the multi-stage duplicate detection process, reference counting is conducted in multi-stages. 
Stage  1 is to read  the segment and block  metadata of snapshots 
to accumulate  reference count requests in different machines  in the fingerprint based distribution.
Stage   2 is to count references within each partition and detect those records with zero 
reference. 
%Stage 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 
its deletion log is too big. 
%Due to the paper constraint, we will not discuss the deletion operations in details.

>>>>

The representation of each snapshot in the backup storage
has a two-level index structure in the form of a hierarchical
directed acyclic graph as shown in Figure~\ref{fig:snapshot}.
A VM image is divided into a set of segments and each  segment contains hundreds of content blocks. 
These blocks are of variable-size, partitioned using
the standard content-based chunking technique with 4KB as the average block size. 
%the standard chunking technique~\cite{similar94} with 4KB as the average block size. 
%To simplify the deduplication process, segments are aligned to fix-sized boundaries, currently using 2MB.
The snapshot metadata  contains a list of segments and other meta data information.
Segment metadata  contains its  content block fingerprints and reference pointers. 
If a segment is not changed from one snapshot to another, indicated by a dirty bit embedded in the virtual disk driver, 
%its content blocks are not changed as well, thus 
its segment metadata contains a reference pointer to an earlier segment.
For a dirty segment, if one of its blocks is duplicate to another block in the system,  
the block metadata contains a reference pointer to the earlier block.

@@

{\bf Snapshot deletion.} Each VM will keep a limited number of  automatically-saved VM snapshots and thus
expired snapshots will be deleted unless its owner explicitly asks for its retention.
We adopt the idea of mark-and-sweep~\cite{Guo2011}. 
A block or a segment can be deleted if its reference count is zero.
%As we discussed in Section~\ref{sect:data}, the reference counter is kept in the global index, partitioned among machines. 
To delete useless  blocks or segments periodically, we read the meta data  of all
snapshots and compute the reference count of all blocks and segments  in parallel
while following the fingerprint-based partitioning.
Similar to the multi-stage duplicate detection process, reference counting is conducted in multi-stages. 
Stage  1 is to read  the segment and block  metadata of snapshots 
to accumulate  reference count requests in different machines  in the fingerprint based distribution.
Stage   2 is to count references within each partition and detect those records with zero 
reference. 
%Stage 3 is that every VM gathers its z confirmed deletion requests for its content and sends them to the backup storage.
The backup  data repository logs deletion instructions,  and will periodically perform a compaction operation when 
its deletion log is too big. 
%Due to the paper constraint, we will not discuss the deletion operations in details.
